A thesis draft

### 2018-10-02 draft.tex
Add content

\section{Technical analysis}

@@

During the testbed development we first tried the TUN/TAP solution, that 
revealed to be not completely transparent and with major performance drawbacks 
(i.e. packet transmission in a LAN connection reached latencies of 50ms) 
\todo{Explain the constraint of point-to-point connections, while we need 
dynamic SFC)}

>>>>

\section{Architecture overview}

During the testbed development the software architecture diverged from the 
original one, experiencing different evolutions and modifications.

\section{SFC packet transmission strategies}

@@

During the testbed development we first tried the TUN/TAP solution, that 
revealed to be not completely transparent and with major performance drawbacks 
(i.e. packet transmission in a LAN connection reached latencies of 50ms) 
\todo{Explain the constraint of point-to-point connections, while we need 
dynamic SFC)}, so we choose to opt for a TCP session recreation solution, 
implementing a little back-end with the aim of saving in a persistent storage 
the SFC the packet has to perform and additional metadata.
